\TheTitle

### 2019-11-22 Paper1/results.tex
minor change

First, let us mention that the adaptive SG method fails, since it yields negative densities during the iteration. The standard SG method however preserves positivity of mass, energy and pressure. The change of the relative L$^2$-error during the iteration to the steady state has been recorded in Figure~\ref{fig:sub31} for the expectation values and in Figure~\ref{fig:sub32}. When comparing intrusive methods without acceleration techniques as well as SC, the following properties emerge:
\begin{itemize}
\item Compared to IPM, stochastic-Galerkin comes at a significantly reduced runtime, meaning that the IPM optimization problem requires a significant computational effort.
\item SG$_9$ shows a smaller error compared to IPM$_9$ for the expectation value. For the variance, we see the opposite, i.e. IPM yields a better solution approximation than SG.
\end{itemize}
The proposed acceleration techniques show the following behavior:
\begin{itemize}
\item The One-Shot IPM (osIPM) method proposed in Section~\ref{sec:OneShotIPM} reduces the runtime while yielding the same error as the classical IPM method.
\item When using adaptivity (see Algorithm~\ref{alg:ad-IPM}) in combination with the One-Shot idea, the method is denoted by \textit{adaptive One-Shot IPM} (adosIPM). This method reaches the steady state IPM solution with a faster runtime than SG.
\item The idea of refinement retardation combined with adosIPM (see Algorithm~\ref{alg:adosIPM}) is denoted by retardation adosIPM (readosIPM), which further decreases runtime. Here, we use two different strategies to increase the accuracy: First, we steadily increase the maximal truncation order when the residual approaches zero. To determine residual values for a given set of truncation orders $2,4,5$ and $8$, we study at which residual level the IPM method reaches a saturated error level for each truncation order. The residual values are then determined to be $6e-05,3e-05,2.2e-5$ and $2e-05$. The second, straight forward strategy converges the solution on a low truncation order of $2$ to a residual of $10^{-5}$ and then switches to a maximal truncation order of $9$. Strategy 1 is depicted in red, Strategy 2 is depicted in green. It can be seen that both approaches reach the IPM$_9$ error for the same run time. Hence, we deduce that a naive choice of the refinement retardation strategy suffices to yield a satisfactory behavior.
\end{itemize}

>>>>

First, let us mention that the adaptive SG method fails, since it yields negative densities during the iteration. The standard SG method however preserves positivity of mass, energy and pressure. The change of the relative L$^2$-error during the iteration to the steady state has been recorded in Figure~\ref{fig:sub31} for the expectation value and in Figure~\ref{fig:sub32} for the variance. When comparing intrusive methods without acceleration techniques as well as SC, the following properties emerge:
\begin{itemize}
\item Compared to IPM, stochastic-Galerkin comes at a significantly reduced runtime, meaning that the IPM optimization problem requires a significant computational effort.
\item SG$_9$ shows a smaller error compared to IPM$_9$ for the expectation value. For the variance, we see the opposite, i.e. IPM yields a better solution approximation than SG.
\end{itemize}
The proposed acceleration techniques show the following behavior:
\begin{itemize}
\item The One-Shot IPM (osIPM) method proposed in Section~\ref{sec:OneShotIPM} reduces the runtime while yielding the same error as the classical IPM method.
\item When using adaptivity (see Algorithm~\ref{alg:ad-IPM}) in combination with the One-Shot idea, the method is denoted by \textit{adaptive One-Shot IPM} (adosIPM). This method reaches the steady state IPM solution with a faster runtime than SG.
\item The idea of refinement retardation combined with adosIPM (see Algorithm~\ref{alg:adosIPM}) is denoted by retardation adosIPM (readosIPM), which further decreases runtime. Here, we use two different strategies to increase the accuracy: First, we steadily increase the maximal truncation order when the residual approaches zero. To determine residual values for a given set of truncation orders $2,4,5$ and $8$, we study at which residual level the IPM method reaches a saturated error level for each truncation order. The residual values are then determined to be $6e-05,3e-05,2.2e-5$ and $2e-05$. The second, straight forward strategy converges the solution on a low truncation order of $2$ to a residual of $10^{-5}$ and then switches to a maximal truncation order of $9$. Strategy 1 is depicted in red, Strategy 2 is depicted in green. It can be seen that both approaches reach the IPM$_9$ error for the same run time. Hence, we deduce that a naive choice of the refinement retardation strategy suffices to yield a satisfactory behavior.
\end{itemize}
